---
title: "Third Markdown Activity"
author: 
- Gian Nicole Villamayor
- Jessica Dela Cruz
- John Lester Santos
- John Rollic Conducto
output: html_document
---

## Introduction
<p>
The profile of the propagation environments as well as the local terrain significantly provide an impact to the performance of the radio waves signals in wireless channels.  Considering these information, the Received Signal Strength (RSS) of the transmitted signals are computed from the distinct data points that are relevant to the radio network planning and optimization.
</p>

## Methodology
<p> **1. Parameter of interest:** The quantity of interest is the
difference in mean reflection voltage, $μ_1 − μ_2$, and $Δ_0 = 0$.


<p> **2. Null hypothesis:** $H_0: μ_1 − μ_2 = 0,$ or $H_0: μ_1 = μ_2.$
<p> **3. Alternative hypothesis:** $H_1: μ_1 > μ_2$. We want to reject $H_0$ if the reflection voltage of the mirror with GaN is significantly lower than the mirror with Gold.
<p> **4. Test statistic:** The test statistic is
$$\Large {t^*_0=\frac{\bar{x_1}- \bar{x_2}-0}{s_p\sqrt{\frac{1}{n_1}+\frac{1}{n_2}} }}$$
<p> **5. Reject** $H_0:μ_1 = μ_2$ **if:** Using α =0.05 and a fixed-significance-level
test, we would reject $H_0:μ_1 = μ_2$ if $t^*_0 < -t_{0.05,967} = -1.65$.
<p> **6. Computations:**
```{r, echo=FALSE}
test1<-read.csv("all.csv")
```
```{r}
t.test(test1$Au,test1$GaN, mu=0, alt="less", conf=0.95, var.equal=F, paired=F)
```
<p> **7. Conclusion:** Because $t^*_0 = -13.399<-t_{0.05,967} = -1.65$, $H_0$ is rejected at the $α = 0.05$ level.
<div class="ans"><p> *Practical Interpretation:* We conclude that semi insulating GaN significantly reduces the reflection voltage of a sapphire surface at millimeter wave frequencies 110-160 Ghz.

## Results and Discussion

```{r, echo=FALSE}
test<-read.csv("range1.csv")
```
```{r}
t.test(test$Au,test$GaN, mu=0, alt="less", conf=0.95, var.equal=F, paired=F)
```

```{r, echo=FALSE}
test<-read.csv("range2.csv")
t.test(test$Au,test$GaN, mu=0, alt="less", conf=0.95, var.equal=F, paired=F)
```

```{r, echo=FALSE}
test<-read.csv("range3.csv")
t.test(test$Au,test$GaN, mu=0, alt="less", conf=0.95, var.equal=F, paired=F)
```

```{r, echo=FALSE}
test<-read.csv("all.csv")
t.test(test$Au,test$GaN, mu=0, alt="less", conf=0.95, var.equal=F, paired=F)
```


### Graphs






