---
title: "Fourth R Markdown"
author: Gian Nicole Villamayor, Jessica Dela Cruz, John Lester Santos, John Rollic
  Conducto
date: "8/6/2021"
output: html_document
---


## cahc {.tabset}

### **Introduction**






### **Methodology**




### **Results and Discussion**
<h3> 900 MHz </h3>

```{r, echo=FALSE}
dt1 = read.csv("sec3_900.csv")
model <- lm(rss ~ elevation + altitude + distance, data = dt1)
summary(model)
```

$$ Signal\:Strength = -74.402204-1.347962\:terrain\:elevation+0.252856\:altitude-0.001454\:distance$$

<h3><b>T-test on each regression coefficient (α=0.05). </h3></b>
<p>**Hypotheses:** </p><br>
$\large H_0:B_0=0,\: H_1:B_0\neq0,\:B_0=intercept$<br>
$\large H_0:B_1=0,\: H_1:B_1\neq0,\:B_1=terrain\:elevation$<br>
$\large H_0:B_2=0,\: H_1:B_2\neq0,\:B_2=altitude$<br>
$\large H_0:B_3=0,\: H_1:B_3\neq0,\:B_3=distance$<br><br>
<p>**Reject** $H_0:B=0$ **if: the P-value is less than 0.05.** </p>
<p>**Test statistic:** </p>
<p>Based from table 2.1</p>
$$\large P_0=7.74*10^-9$$
$$\large P_1=0.019$$
$$\large t_2=0.763$$
$$\large t_3=0.460$$
<p>Conclusion: The researchers only reject the null hypothesis for $B_1$. 
<p>*Practical Interpretation:* Altitude is the only significant to the model </p> 

<h3> 1800 MHz </h3>

```{r, echo=FALSE}
dt1 = read.csv("sec3_1800.csv")
model <- lm(rss ~ elevation + altitude + distance, data = dt1)
summary(model)
```










### **References**



<br>
<br>
<br>

```{css, echo = FALSE}
p {
  font-size: 15px;
}
```
